\chapter{Acknowledgement}

Many thanks to Prof.~Donald Knuth for giving us \TeX, and Leslie Lamport for \LaTeX.  

I first learned \LaTeX{} as an undergraduate student in Computer Science at the University of Warwick. Back in Malaysia, I picked it up again while doing my M.Sc.~at USM, as part of some productive procrastination (there I've admitted it!!). This coincided with Dr.~Dhanesh's and Dr.~Azman's efforts in raising awareness about \LaTeX{} at USM during NaCSPC'05 -- somehow one thing led to another, and I now conduct trainings and consultatons on \LaTeX. \Smiley

Since then, many friends and fellow \LaTeX{} users have given feedback and helped relayed important updates from IPS to me, to help improve the class and template. It has actually come to a point where you are too numerous to name! Thank you all, as well as everyone who has attended my talks and workshops, used my various templates, downloaded examples from my website (\url{http://liantze.penguinattack.org/latextypesetting.html}).

Hope everyone graduates quickly then!

\texttt{Joseph Ooi:} Many thanks to LianTze Lim and \texttt{wnarffin} for maintaining the GitHub repo which contains the \LaTeX{} template, without which my attempt at reproducing the likeness of the latest thesis template version from USM would be unachievable. Here's to hoping more people taste the forbidden fruit that is \LaTeX{} and forsake Microsoft Office Word. Happy \LaTeX{}-ing everyone! 

\texttt{Joseph Ooi:} By the way, don't worry about if warnings that the hyper reference to some of your defined acronyms not being defined pop up. They should go away once you use 
those acronyms via \verb|\ac{...}| or \verb|\acs{...}| or \verb|\acf{...}| or something else at least once in your text. Or you can just ignore them.

%Thanks to Dr.~Donald Knuth for giving us \TeX, Leslie Lamport for \LaTeX, the NaCSPC'05 committee and Dr.~Dhanesh for spreading the \LaTeX word and material.

%Hope everyone graduates quickly!